---
title: "Chapter3"
output: html_notebook
---

# Conceptual

## Problem 2

KNN Regression attempts to estimate E[Y|X1...Xp] using the local average. KNN Classification attempts to estimate P(Y|x1...Xp) using local probability.

## Problem 3

+ a \
female = 1, male = 0 \
full equation: starting salary = $50 + 20*GPA + 0.07*IQ + 35*Gender + 0.01*GPA*IQ -10*GPA*Gender$ \
(gender = female): $85 + 10*GPA + 0.07*IQ + 0.01*GPA*IQ$ \
(gender = male):   $50 + 20*GPA + 0.07*IQ + 0.01*GPA*IQ$ \

solving $50 + 20*GPA > 85 + 10*GPA$ => gpa > 3.5 males on average will have higher starting salaries. (iii)

+ b \
85 + 10(4.0) + 0.07(110) + 0.01(4.0)(110) = 137.1, which gives us a starting salary of $137,100

+ c \
False, we need to do a hypothesis test $\hat{\beta_4} = 0$

## Problem 4

+ a \

We expect the linear model  to have a lower RSS, since the true model is linear.

+ b \

Not enough information, if the test data is close to the training, we would expect the RSS to be lower for the linear model.

+ c \

Not enough information

 + d \
 
 Not enough information
 
 ## Problem 10
```{r include=FALSE, echo=FALSE}
library(tidyverse)

data(Carseats, package = "ISLR")

Carseats %>% 
  janitor::clean_names() -> df

mod1 <- lm(sales ~ price + urban + us, data = df)
```

+ a

```{r}
jtools::summ(mod1, digits = 4)
```
 
 + b \
Holding all other predictors fixed, for a $1 dollar increase in price, average unit sales decrease by 54.5 units in sales. \
the average sales for non-urban is estimated to be 13043.5, whereas urban are estimated to carry a decrease of 21.9 unit sales for an estimate of 13021.1 units. The P-value is high, this indicates that there is no statistical evidence of a difference in  average unit sales between urban and non-urban areas. \
The average unit sales for non-US stores is estimated to be 13043.5, whereas US stores are estimated to carry 1200.6 additional unit sales for an estimate of 14244.1 unit sales. The P-value is small, this indicates that there is statistical evidence of a difference in average unit sales between US stores and non-US stores.


+ c \
$sales = 13.0435 + -0.0545*price + -0.0219*urban + 1.2006*us$

+ d \
rej H0 for price and US

+ e \

table below

+ f \
model without Urban variable has a higher R2 and lower s, we can say about 24% of the sample variation in unit sales is explained by this model, and approximately 95% of unit sales fall within $\pm$ 4.938 (2s) of there respected predicted values.

+ g \
table below
```{r}
mod2 <- lm(sales ~ price + us, data = df)

jtools::summ(mod2, confint = TRUE, vif = TRUE)
```

h \
From the residual plots, we can see evidence  of outliers and influential observations using the sresiduals vs leverage plot, as well as, the residuals vs fitted values plot.
```{r}
plot(mod2) # Residual Plots for model 2

mean_leverage <- as.data.frame(hatvalues(mod2)) %>% 
  summarise(mean = mean(`hatvalues(mod2)`))

# 20 influential points
as.data.frame(hatvalues(mod2)) %>% 
  filter(`hatvalues(mod2)` > 0.015) %>% 
  rename(leverage = `hatvalues(mod2)`)
```


